Quantifying the ease of viral escape from broad and narrow antibodies to influenza hemagglutinin

### 2017-10-13 paper/manuscript.tex
Added a few sentences to various results sections

In order to compare the potencies of these antibodies, we completed GFP-based neutralization assays using wild-type A/WSN/1933 (H1N1) virus. 
Figure~\ref{fig:neutcurves} shows the neutralization curves for each antibody, and all six antibodies show similar potencies.

@@

It is immediately obvious that both the three strain-specific antibodies and the antibody targeting HA's receptor-binding pocket (S139/1) select antigenic mutations with large effects at multiple sites.
Specifically, Figure~\ref{fig:avgfracsurvive} shows that for all four of these antibodies, there are sites where a substantial fraction of virions with any mutation survive antibody concentrations that are far in excess of those needed to nearly complete neutralize the wildtype virus.

\subsection*{For all antibodies, the selected sites of escape occur in the antibody binding footprints}

>>>>

In order to compare the potencies of these antibodies, we completed GFP-based neutralization assays using wild-type A/WSN/1933 (H1N1) virus. 
Figure~\ref{fig:neutcurves} shows the neutralization curves for each antibody, and all six antibodies show similar potencies.
We chose to conduct the library selections with concentrations of antibodies that would neutralize nearly all wildtype viruses.

@@

It is immediately obvious that both the three strain-specific antibodies and the antibody targeting HA's receptor-binding pocket (S139/1) select antigenic mutations with large effects at multiple sites.
Specifically, Figure~\ref{fig:avgfracsurvive} shows that for all four of these antibodies, there are sites where a substantial fraction of virions with any mutation survive antibody concentrations that are far in excess of those needed to nearly complete neutralize the wildtype virus.
% Worth mentioning how some escape mutants from H17L19 have reduced fraction escape at the higher concentration, while this is not seen for S139/1?

In contrast, the stalk-targeting antibodies...

\subsection*{For all antibodies, the selected sites of escape occur in the antibody binding footprints}
We visualized for each mutation the fraction surviving selection as a logoplot, and mapped the mutation with the maximum fraction surviving selection at each site onto the HA structure, shown in Figure~\ref{fig:structures}.
